---
title: "ggparliament: Parliament Plots in the Tidyverse"
author: 
- "Zoe Meers" 
- "twitter: https://twitter.com/zoe_meers"
- "email: zoe.meers@sydney.edu.au"
date: "June 20, 2018"
output: 
  ioslides_presentation:
    logo: template/ussc_logo.png
    template: template/ussc_ioslides.html
    css: template/ussc_styles.css
    widescreen: true
    smaller: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ussc)
library(tidyverse)
library(emo)
```


## Uh... What are parliament plots? `r emo::ji("confused")`

- They are visual representations of the composition of legislatures.


- Parliament plots often display seats color-coded by party


- This is one the first attempts at creating an `R` package for parliament plots

## ggparliament
- ggparliament was first started by Thomas Leeper


- I, along with Rob Hickman, have taken over the package


- The idea is that it creates `ggplot2` objects of parliamentary seats that integrate seamlessly with other `Tidyverse` packages


- Currently working on the development version of the package
  - We can plot several parliament "styles" ranging from the horseshoe parliament (like the one we have here!) or two opposing benches (like the in UK)
  
  
- ggparliament is not on CRAN (yet!)

## Great...`r emo::ji("smile")` How can we use it?

- Start with aggregated election results. 


- We have included data from several countries several in the package. 


- For example, I will look at the Australian 2016 election.


- The data frame looks like this ...


## 
```{r}
# library(ggparliament)
# australia <- election_data %>%
#   filter(year == 2016 &
#            country == "Australia" & 
#            house == "Representatives")
# head(australia)
```
## Data munging
- We want to expand the aggregated seats per party into a long list of individual seats and plot the location of each seat on the chart


- We have created a function -- `parliament_data()` -- that will do this for you!


##

```{r}
# run your election results through parliament_data()
# australia <- australia[c(1, 5, 6, 7, 4, 3, 2), ]
# aus <- parliament_data(election_data = australia, # you need to specify the data frame
#                        total_seats = sum(australia$seats), # sum up the total amount of seats
#                        party_seats = australia$seats, # number of seats per party
#                        parl_rows = 4, # how many rows do we want?
#                        type = "horseshoe") # what type of parliament do we want?
# head(aus)
```

## Now... The fun stuff `r emo::ji("smile")`
```{r}
# ggplot(aus, aes(x, y, colour=party_long)) + #define the data frame and how you want to colour the circles
#   geom_parliament_seats() + # this geom plots the seats
#   theme_parliament() + # we have created a theme for the package but this is optional
#   labs(colour = "", title = "Australia House of Representatives") +
#   scale_colour_manual(values = aus$colour, limits = aus$party_long)
```
## Cool. What else?
- We can highlight certain seats!


- This is a work in progress


- We can add text to the plot designating the number of Representatives in the parliament

## 

```{r}
 # ggplot(aus, aes(x, y, colour=party_long)) +
 #   geom_parliament_seats() +
 #   theme_parliament() +
 #   geom_highlight_government(government == 1) +
 #   labs(colour = "", title = "Australia House of Representatives",
 #   subtitle = "Government encircled in black.") +
 #   annotate("text", x=0, y=0, label=paste("Total: 150 MPs"), fontface="bold", size=12) +
 #   scale_colour_manual(values = aus$colour, limits = aus$party_long)
```

